Project assignment - Tahoe-LAFS with SHA-3 candidates

### 2010-12-06 paper/main.tex
Added List of Listings and fixed page numbering of pre chapters
Keywords on what to fill out in the report

\addcontentsline{toc}{chapter}{\listfigurename} % Manually add to ToC
\listoffigures

\addcontentsline{toc}{chapter}{\listtablename}
\listoftables

@@

\section{Distribution of the Code}
% Distutil, bash scripts

@@

\subsection{\ac{SUPERCOP} benchmarks}
The results of \ac{SHA}-3
256-bit functions and \ac{SHA}-256 benchmarking in \ac{SUPERCOP} can be seen in
tables \ref{tbl:supercop:long}, \ref{tbl:supercop:4096},
\ref{tbl:supercop:1536}, \ref{tbl:supercop:576}, \ref{tbl:supercop:64} and
\ref{tbl:supercop:8}. The lower the numbers, the faster the algorithms
performed in the test.

@@

What is tested and what is not tested?

How much time is spent on hashing versus upload over network?

How much gain can Tahoe-LAFS get by switching to SHA-3?

Plenty of tables, graphs

@@

What could have been done differently?

Compare results with general (supercop) results.

Optimized candidates.

What if we had used another coding scheme?

Implications of only testing immutable files?

Adding a capability to support new hash functions in tahoe.

>>>>

\cleardoublepage
\phantomsection
\addcontentsline{toc}{chapter}{\listfigurename}
\listoffigures

\cleardoublepage
\phantomsection
\addcontentsline{toc}{chapter}{\listtablename}
\listoftables

\cleardoublepage
\phantomsection
\addcontentsline{toc}{chapter}{\lstlistlistingname}
\lstlistoflistings
\cleardoublepage

@@

\section{Distribution of the Code}
% TODO: Distutil, bash scripts

@@

\begin{itemize}
    \item Section should only contain the hard facts of our measurements
    \item What is tested and what is not tested?
    \item How much time is spent on hashing versus total time of
    uploading/downloading
    \item How much gain can Tahoe-LAFS get by switching to SHA-3?
\end{itemize}

\section{\ac{SUPERCOP} benchmarks}
The results of \ac{SHA}-3
256-bit functions and \ac{SHA}-256 benchmarking in \ac{SUPERCOP} can be seen in
tables \ref{tbl:supercop:long}, \ref{tbl:supercop:4096},
\ref{tbl:supercop:1536}, \ref{tbl:supercop:576}, \ref{tbl:supercop:64} and
\ref{tbl:supercop:8}. The lower the numbers, the faster the algorithms
performed in the test.

@@

@@

\begin{itemize}
    \item What could have been done differently?
    \item Compare our results with general (supercop) results.
    \item Optimized candidates - which gain could be expected from more
    optimized candidates
    \item What if we had used another coding scheme? - does Cython lower the
    candidates performance?
    \item Implications of only testing immutable files? (mutable files also
    include directories)
    \item Adding a capability to support new hash functions in tahoe. (Our
    current way breaks backwards compatability)
\end{itemize}
